\texttt{ensmallen}: a flexible C++ library for efficient function optimization

### 2018-10-15 doc/mlsys_paper/paper.tex
improvements and suggestions for further details

\vspace*{-0.3em}
\section{Available optimizers}
\vspace*{-0.5em}

Due to the easy abstraction, {\tt ensmallen} is able to provide a large set of
diverse optimization algorithms.  Below is a list of what is currently
available.

% I guess to save some space we should group them.
\vspace*{-0.4em}
\begin{itemize}
  \item {\bf SGD variants:} Stochastic Gradient Descent (SGD), Stochastic
      Coordinate Descent (SCD), Parallel Stochastic Gradient Descent (Hogwild!),
      Stochastic Gradient Descent with Restarts (SGDR), SMORMS3, AdaGrad,
      AdaDelta, RMSProp, Adam, AdaMax

@@

In addition, many optimization algorithms are currently in development and will
be released in the future.

>>>>

\vspace*{-0.3em}
\section{Available Optimizers}
\vspace*{-0.5em}

Due to the straightforward abstraction framework, {\tt ensmallen} is able to
provide a large set of diverse optimization algorithms.  Below is a list of
currently available optimizers:

% I guess to save some space we should group them.
%% CS: should we add citations to some (or all) of the listed optimisers?
%% CS: the MLSYS CFP states that "papers can be up to 6 pages (not including references)",
%% CS: so technically we can have 10000+ references.
\vspace*{-0.4em}
\begin{itemize}
  \item {\bf SGD variants:} Stochastic Gradient Descent (SGD), Stochastic
      Coordinate Descent (SCD), Parallel Stochastic Gradient Descent (Hogwild!),
      Stochastic Gradient Descent with Restarts (SGDR), SMORMS3, AdaGrad,
      AdaDelta, RMSProp, Adam, AdaMax

@@

%% CS: "in development" is ambiguous here;
%% CS: is it in development by AI/ML researchers in general,
%% CS: or by ensmallen developers/contributors?
% In addition, many optimization algorithms are currently in development and will
% be released in the future.

%% CS: less ambiguous proclamation that has similar effect:
We aim to expand {\tt ensmallen} with further optimization techniques
as the need arises.  Since {\tt ensmallen} is open source,
external contributions to the codebase are welcome.
